### 2017-03-24 paper/oopsla17-submission/evaluation-utility.tex
more eval

\autoref{tab:contextual-features} summarizes the results of our experiment.
%
As we can see, the \linear classifier and the \hiddenFH start off
competitive when given only local syntactic features, but the \hiddenFH
quickly begins to outperform as more features are added.
%
\ES{HEREHEREHERHE}

>>>>

\paragraph{Results}
\autoref{tab:contextual-features} summarizes the results of our experiment.
%
As we can see, the \linear classifier and the \hiddenFH start off
competitive when given only local syntactic features, but the \hiddenFH
quickly begins to outperform as more features are added.

\ExprSize appears to be the weakest feature, improving \linear Top-1
accuracy by only 1\% and \hiddenFH by only 4\%.
%
In contrast, the contextual syntactic features improve \linear Top-1
accuracy by 5\% (\resp 15\%), and the typing features improve
Top-1 accuracy by 7\% (\resp 17\%).
%
Furthermore, while \ExprSize does provide some benefit when it is the
only additional feature, it does not appear to provide any real increase
in accuracy when added alongside the contextual or typing features.

As one might expect, the typing features are more beneficial than the
contextual syntactic features.
%
They improve Top-1 accuracy by an additional 2\%, and are much more
compact --- we only have 55 typing features compared to 176 contextual
syntactic features.
%
This aligns with our intuition that types should be a good summary of
the context of an expression.
%
However, typing features do not \emph{subsume} contextual syntactic
features, we can gain an additional 1\% Top-1 accuracy (\resp 4\%) by
adding \emph{both}.
